Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-24 paper/ms.tex
intro + methods basically good

\begin{figure*}[!t]
	\gridline{
    \fig{raw_light_curve_systematics_sec6cam1ccd2.pdf}{0.48\textwidth}{}
    \fig{raw_light_curve_systematics_sec7cam2ccd4.pdf}{0.48\textwidth}{}
  }
	\vspace{-0.5cm}
	\caption{
	Twenty randomly selected raw image-subtracted light curves drawn
	from the same sector, camera,
	and CCD, for stars with $T$-band magnitudes between 13 and 14.
	A number of systematic trends are shared across the light curves.
	The sector, camera, and CCD numbers are 6, 1, 2 (left) and 7, 2, 4 (right).
	\label{fig:lc_systematics}
	}
\end{figure*}

@@

The preceding steps produce light curves that include both
instrumental systematics as well as astrophysical variability.
Figure~\ref{fig:lc_systematics} shows twenty stars of
comparable brightness randomly selected from two CCDs.  Stars that are
far apart on the same CCD share similar changes in flux.
In other words, the instrumental systematics seem to dominate.
This problem is generic to most wide-field photometric datasets, including
those from {\it e.g.}, the WASP, HAT, and Kepler surveys.
To remove the systematic variability, we adopted two different
approaches: {\it (i)} the trend-filtering algorithm (TFA,
\citealt{kovacs_trend_2005}), and {\it (ii)} a principal component analysis
(PCA).

>>>>

\begin{figure*}[!t]
	\gridline{
    \fig{raw_light_curve_systematics_sec6cam1ccd2.pdf}{0.48\textwidth}{}
    \fig{raw_light_curve_systematics_sec7cam2ccd4.pdf}{0.48\textwidth}{}
  }
	\vspace{-0.5cm}
	\caption{
	Twenty randomly selected stars drawn
	from the same sector, camera,
	and CCD, for stars with $T$-band magnitudes between 13 and 14.

  %#FIXME CAPTIOIN
raw image-subtracted light curves

	A number of systematic trends are shared across the light curves.
	The sector, camera, and CCD numbers are 6, 1, 2 (left) and 7, 2, 4 (right).
	\label{fig:lc_systematics_detrended}
	}
\end{figure*}

@@

The preceding steps produce light curves that include both
instrumental systematics as well as astrophysical variability.
Figure~\ref{fig:lc_systematics_detrended} shows twenty stars of
comparable brightness randomly selected from two CCDs.  Stars that are
far apart on the same CCD share similar changes in flux.
In other words, the instrumental systematics seem to dominate.
This problem is generic to most wide-field photometric datasets, including
those from {\it e.g.}, the WASP, HAT, and Kepler surveys.
To remove the systematic variability, we adopted two different
approaches: {\it (i)} the trend-filtering algorithm (TFA,
\citealt{kovacs_trend_2005}), and {\it (ii)} a principal component analysis
(PCA).
